---
output: github_document
Knit: (function(input_file, encoding) {
  out_dir <- '';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'README.html'))})

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```



# Yan & Henck Inspo 

## Installation

You can install bestinbloom from GitHub with:

```{r install, message=FALSE, warning=FALSE, eval=FALSE}
# install.packages("devtools")
devtools::install_github("arsweeny/bestinbloom")
```

## Usage 

You can create a palette with the following command, specifying type ("qual", "seq", "div")

```{r load}
library(bestinbloom)
```


```{r results = 'show'}
pal <- bloom_palette("Episode3", type="qual")
```

If you want a specific number of colors up to 6 (qual), 8 (seq), 9 (div)

```{r}
pal <- bloom_palette("Episode3", type="qual", n=4)
```


## Palettes Available 

Palettes in this package correspond to Yan & Henck's outfits in each episode of The Big Flower Fight Season1, named accordingly. 

```{r setUp, include=FALSE}
library(png)
library(tidyverse)
library(RImagePalette)

PalPath <- "/Users/asweeny/bestinbloom/Outfits/"
PalPics <- list.files(PalPath) %>% as.data.frame() %>% 
  mutate_at(vars(.), as.character) %>% 
  pull(.) #remove the master image 

PalNames <- str_remove(PalPics, ".png") #Palette Names 
PalPaths <- paste0(PalPath, PalPics)

Eps<- list()
for(i in 1:length(PalPaths)){
  Eps[[i]] <- readPNG(PalPaths[[i]])
}

QualBlooms <- readRDS('/Users/asweeny/bestinbloom/Palettes/QualBlooms.rds')
#SeqBlooms <- readRDS('Palettes/SeqBlooms.rds')
#DivBlooms <- readRDS('Palettes/DivBlooms.rds')
```

```{r print function, include=FALSE}
print.palette <- function(x, ...) {
  n <- length(x)
  old <- par(mar = c(0.5, 0.5, 0.5, 0.5))
  on.exit(par(old))

  image(1:n, 1, as.matrix(1:n), col = x,
        ylab = "", xaxt = "n", yaxt = "n", bty = "n")

  rect(0, 0.9, n + 1, 1.1, col = rgb(1, 1, 1, 0.8), border = NA)
  text((n + 1) / 2, 1, labels = attr(x, "name"), family = "Helvetica", col = "black")
}
```


### Episode 1
```{r Ep 1, echo=FALSE}
display_image(Eps[[1]])
print.palette(QualBlooms[[1]])
```

### Episode 2
```{r Ep 2, echo=FALSE}
display_image(Eps[[2]])
print.palette(QualBlooms[[2]])
```

### Episode 3
```{r Ep 3, echo=FALSE}
display_image(Eps[[3]])
print.palette(QualBlooms[[3]])
```

### Episode 4 
```{r Ep 4,  echo=FALSE}
display_image(Eps[[4]])
print.palette(QualBlooms[[4]])
```

### Episode 5 
```{r Ep 5,  echo=FALSE}
display_image(Eps[[5]])
print.palette(QualBlooms[[5]])
```

### Episode 6 
```{r Ep 6,  echo=FALSE}
display_image(Eps[[6]])
print.palette(QualBlooms[[6]])
```

### Episode 7 
```{r Ep 7, echo=FALSE}
display_image(Eps[[7]])
print.palette(QualBlooms[[7]])
```

### Finale
```{r Finale, echo=FALSE}
display_image(Eps[[8]])
print.palette(QualBlooms[[8]])
```


